### 2016-01-16 urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
to send out tomorrow

We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\cite{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. It provides a new understanding of the interaction between human activity and urban structures. 
%NOTE: I'm not sure how twitter relates to urban structure...

%NOTE: I did not review the figures or figure captions
\section*{Materials and Methods}
\subsection*{Overview}
We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

@@

\section*{Conclusion}
In this study, we delineated the non-administrative anthropographic urban boundaries within the United Kingdom using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
Then by studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in the United Kingdom. 
Twitter user movements were used to establish a connectivity network of the fishnet cells.
Then we applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries of the United Kingdom.
By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.

>>>>

We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\cite{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. It provides a new understanding of the interaction between human activity and urban structures.

\section*{Materials and Methods}
\subsection*{Overview}
We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

@@

\section*{Conclusion}
In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
Then by studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in the United Kingdom. 
Twitter user movements were used to establish a connectivity network of the fishnet cells.
Then we applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries of the United Kingdom.
By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.
